Eye in a Disk: eyeIntegration human pan-eye and body transcriptome database version 1.00

### 2019-03-01 manuscript.Rmd
text changes
sup figs added

We plotted these sets of genes 
Analysis of broad trends in GO term enrichment between differentially expressed genes shows that the HOXB family and protocadherins are differentially expressed between fetal retina and organoids. We noticed that several BRN3/POU4F genes were also differentially regulated

@@

@@

```{r GOterm_fetal_retina_organoid, echo = F, results='asis', warning = F, fig.cap = GOterm_cap, fig.pos = 'H'}
GOterm_cap <- supTab_cap(name='GOterm_fetal_retina_organoid', caption = 'Top GO terms enriched between fetal retina and organoid retina, after paring of redundant terms with REVIGO')
# Output <div>
cat("<div id=\"tbl:GOterm_fetal_retina_organoid\">")
organoid_fetal_GO %>% filter(ID %in% c('GO:0001503','GO:0031589','GO:0050878','GO:0061448','GO:0050678','GO:0030335','GO:0030198', 'GO:0007156', 'GO:0050769', 'GO:0030099')) %>% mutate(geneID = gsub('<br>', ' ', geneID)) %>% as_tibble() %>% regulartable() %>% 
  flextable::align(align='center') %>% 
  font(fontname = 'Linux Libertine O', part = 'all')
#Output Caption (* * for italics)
cat(paste0("\n*",GOterm_cap,"*\n"))
# Output </div>
cat("</div>")
```
# Acknowledgements

>>>>

We plotted these three sets of genes in the heatmap view, with columns as age in days of fetal or organoid retina and rows are genes. We see that there are strong, consistent gene expression changes in these three groups of genes between fetal retina and the organoid samples (`r paste0(fig_cap(name = 'rgc_cadherin_hoxb', display = 'cite'))`). We also plot the differential expression differences between all organoids and all fetal retina samples; all genes across all three sets are significantly differentially expressed with a FDR corrected p value < 0.01.

@@

```{r rgc_cadherin_hoxb, echo = F, message = F, warning=F, fig.width = 10, fig.pos='H', fig.cap = snakemakeDAG_cap}
rgc_cadherin_hoxb_cap <- supFig_cap(name='rgc_cadherin_hoxb', caption = 'Heatmap of three sets of genes across fetal retina and organoids divided by age in days (A). Bar plot of differential expression from retina to organoid, where positive values are genes that are higher expressed in fetal tissue than organoid. All logFC expression values have FDR corrected p value  < 0.01.')

knitr::include_graphics('figures_and_tables/rgc_cadheren_box_fig.png')
```

@@

```{r GOterm_fetal_retina_organoid, echo = F, results='asis', warning = F, fig.cap = GOterm_cap, fig.pos = 'H'}
GOterm_cap <- supTab_cap(name='GOterm_fetal_retina_organoid', caption = 'Top GO terms enriched between fetal retina and organoid retina, after paring of redundant terms with REVIGO')
# Output <div>
cat("<div id=\"tbl:GOterm_fetal_retina_organoid\">")
organoid_fetal_GO %>% 
  dplyr::select(-ONTOLOGY, -BgRatio, -p.adjust, -Count, -Test, -Set) %>% 
  filter(ID %in% c('GO:0001503','GO:0031589','GO:0050878','GO:0061448','GO:0050678','GO:0030335','GO:0030198', 'GO:0007156', 'GO:0050769', 'GO:0030099')) %>% 
  mutate(geneID = gsub('<br>', ' ', geneID)) %>% 
  as_tibble() %>% 
  regulartable() %>% 
  flextable::fontsize(size = 8) %>% 
  width(width = c(1,1,1,1,1,2)) %>% 
  flextable::align(align='center') %>% 
  font(fontname = 'Linux Libertine O', part = 'all') 
#
#Output Caption (* * for italics)
cat(paste0("\n*",GOterm_cap,"*\n"))
# Output </div>
cat("</div>")
```
# Acknowledgements
